Modeling the Linux page cache for accurate simulation of data-intensive applications

### 2020-12-10 paper_io_sim.tex
small things

\author{
  \IEEEauthorblockN{
    Hoang-Dung Do\IEEEauthorrefmark{1},
    Val\'erie Hayot-Sasson\IEEEauthorrefmark{1},
    Rafael Ferreira da Silva\IEEEauthorrefmark{3},
    Christopher Steele\IEEEauthorrefmark{4}
    Henri Casanova\IEEEauthorrefmark{2},
    Tristan Glatard\IEEEauthorrefmark{1}
  }\\
  \IEEEauthorblockA{
    \IEEEauthorrefmark{1}Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada\\
    \IEEEauthorrefmark{2}Department of Information and Computer Sciences, University of Hawai`i at M\=anoa, USA\\
    \IEEEauthorrefmark{3}Information Sciences Institute, University of Southern California, Marina Del Rey, CA, USA\\
    \IEEEauthorrefmark{4}Department of Psychology, Concordia University, Montreal, Canada
  }
}

@@

        The real application is a workflow of the Nighres
        toolbox~\cite{huntenburg2018nighres} that implements skull
        stripping in high-resolution brain images, an operation common to
        many analysis pipelines. The workflow is implemented as a Python
        script that calls Java image-processing routines. We used Python
        3.6, Java 8, and Nighres \tristan{add version}. We patched the
        skull stripping workflow to monitor task CPU times and inject them
        in the simulation, to focus our analysis on I/O times \tristan{add
        link to patched code}.

>>>>

\author{
  \IEEEauthorblockN{
    Hoang-Dung Do\IEEEauthorrefmark{1},
    Val\'erie Hayot-Sasson\IEEEauthorrefmark{1},
    Rafael Ferreira da Silva\IEEEauthorrefmark{3},
    Christopher Steele\IEEEauthorrefmark{4},
    Henri Casanova\IEEEauthorrefmark{2},
    Tristan Glatard\IEEEauthorrefmark{1}
  }\\
  \IEEEauthorblockA{
    \IEEEauthorrefmark{1}Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada\\
    \IEEEauthorrefmark{2}Department of Information and Computer Sciences, University of Hawai`i at M\=anoa, USA\\
    \IEEEauthorrefmark{3}Information Sciences Institute, University of Southern California, Marina Del Rey, CA, USA\\
    \IEEEauthorrefmark{4}Department of Psychology, Concordia University, Montreal, Canada
  }
}

@@

        The real application is a workflow of the Nighres
        toolbox~\cite{huntenburg2018nighres} that implements skull
        stripping in high-resolution brain images, an operation common to
        many neuroimage analysis pipelines. The workflow is implemented as a Python
        script that calls Java image-processing routines. We used Python
        3.6, Java 8, and Nighres \tristan{add version}. We patched the
        skull stripping workflow to monitor task CPU times and inject them
        in the simulation, to focus our analysis on I/O times \tristan{add
        link to patched code}.
